Labeled object representation and manipulation with ITK

### 2007-09-18 article/Article.tex
a note about how to fix sources after the changes of the class names
darcs-hash:20070918095841-2fc9d-74591518f8642e30dec758a1caad59afc8b30bd3.gz

>>>>

Note that some names have been changed in revision 3. To fix your sources, the following commands can be used in your source directory:
\small \begin{verbatim}
perl -e 's/LabelCollectionImage/LabelMap/g' -pi *
perl -e 's/GetNumberOfObjects/GetNumberOfLabelObjects/g' -pi *
perl -e 's/PrintObjects/PrintLabelObjects/g' -pi *
\end{verbatim} \normalsize
